Median Maximum Pairwise Distance

### 2020-10-07 main.Rmd
introduction, principle and structure

Here, we have two main objectives:

@@

# Building a new metric

@@

With reference to the graphical design in \ref{@paper-gravitas}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of facet variables.

>>>>

Here, we aim to build a new measure to follow through these two main objectives:

@@

# Median Maximum Pairwise Distances (MMPD)

@@

With reference to the graphical design in \ref{@paper-gravitas}, therefore the idea would be to rate a harmony pair higher if the variation between different levels of the x-axis variable is higher on an average across all levels of the facet variables. Thus the metric could be obtained by computing maximum pairwise distances between distributions of the continuous random variable across x-axis categories for all facets and then taking the median of those maximum pairwise distances across facets. This would help capture the average maximum difference in distribution of the measurement variable explained by the two cyclic granularities together. We call this metric MMPD which stands for Median Maximum Pairwise Distances. In the next section we shall see how we go about computing this measure.
